---
title: "Lab9_18BCE1010"
output: html_document
---
# Name: R. Harini

# Reg No: 18BCE1010

# Dataset: Life Expectancy rate for different Countries by WHO

```{r setup, include=FALSE}
rm(list=ls())
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(reshape2)
library(car)
```


```{r}
data=read.csv("Life_Expectancy_Data.csv", stringsAsFactors = TRUE)
```

```{r}
summary(data)
str(data)
head(data)
```
### Data Cleaning
```{r}
sum(is.na(data))
```

```{r}
data=data%>%
  drop_na()%>%
  filter(!is.na(Life.expectancy), !is.na(Adult.Mortality), !is.na(infant.deaths))
sum(is.na(data))
```
### Exploratory Data Analytics

```{r}
data%>%
  group_by(Status)%>%
  summarize(count=n(), avg_life_exp=mean(Life.expectancy),avg_inf_mort=mean(infant.deaths), avg_adul_mort=mean(Adult.Mortality))
```

#### Finding the number of Developed and Devloping Countries
```{r}
unique(data$Country)
table(data$Status)
```

#### Find average of Life Expectancy over 15 years for each country
```{r}
data%>%
  group_by(Country)%>%
  summarise(Avg_life_expectancy=round(mean(Life.expectancy)))
```


#### Picking any 3 developed and developing countries
```{r}
dd=data%>%
  filter(Country %in% c('Austria','Belgium','Croatia'))

di=data%>%
  filter(Country %in% c('Brazil','Iraq','India'))

```

#### Plotting Developed Countries
```{r}
p1=ggplot(dd, aes(Year, percentage.expenditure))+geom_smooth(aes(color=Country), se=FALSE)+facet_grid(Country~.)

p2=ggplot(dd, aes(Year, Life.expectancy))+geom_smooth(aes(color=Country), se=FALSE)+facet_grid(Country~.)

grid.arrange(p1,p2,nrow=1)

```
#### Plotting Developing Countries
```{r}
p1=ggplot(di, aes(Year, percentage.expenditure))+geom_smooth(aes(color=Country), se=FALSE)+facet_grid(Country~.)

p2=ggplot(di, aes(Year, Life.expectancy))+geom_smooth(aes(color=Country), se=FALSE)+facet_grid(Country~.)

grid.arrange(p1,p2,nrow=1)
```
#### Visualise Population of countries
```{r}
ggplot(dd,aes(x=Country, y=Population,fill=Country))+geom_bar(stat="identity")
```
```{r}
ggplot(di,aes(x=Country, y=Population,fill=Country))+geom_bar(stat="identity")
```

#### 
```{r}
ggplot(rbind(dd,di), aes(x=percentage.expenditure, y=Total.expenditure, col=Country))+geom_point()+facet_wrap(~Country)+ggtitle("Percentage Expenditure vs Total Expenditure")+xlab("Percentage Expenditure")+ylab("Total Epxenditure")+theme_minimal()
```


#### Scatter plot between BMI and alcohol
```{r}
ggplot(data, aes(BMI, Alcohol, col=Status))+geom_point()+ggtitle("Alcohol vs BMI")
```
#### Performing ANOVA
```{r}
a=aov(Life.expectancy~Status, data)
summary.aov(a)
leveneTest(Life.expectancy~Status, data)
```

#### Correlation between diseases
```{r}
d=data%>%
  drop_na()%>%
  select(Hepatitis.B, Polio, Measles, HIV.AIDS, Diphtheria)

c=cor(d)
m=melt(c)
ggplot(m)+geom_tile(aes(Var1, Var2, fill=value))
```

```{r}
m1=lm(Life.expectancy~., data=data)
summary(m1)
```

```{r}
plot(m1)
```

