---
title: "LabEx4-Data Cleaning in R"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010

### Name:R. Harini

## Setup

```{r}
rm(list=ls())
```

### Load packages if any using library(packagename)
```{r}
library(tidyr)
library(dplyr)
```


### Load data
```{r}
data=read.csv("loans data.csv", stringsAsFactors = FALSE)

```
### Clean the data by including appropriate comments

```{r}
str(data)
```

```{r}
summary(data)
```




* * *

# Data Cleaning

```{r}
#replacing NA values in Amount Requested with mean (Amt requested)

summary(data$Amount.Requested)
```



* * *

##  Frame any 5 Questions on data manipulation and Corresponding Code & Output

```{r}

```
```{r}
#Display the loan length for interest rates above 10%
data%>%
  filter(Interest.Rate>10)%>%
  dplyr::select(Loan.Length, Interest.Rate)
```

```{r}

```


* * *


NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button) above. Make sure that your code is visible
in the file you submit. Delete this note when before you submit your work.


