---
title: "FAT_LAB"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010

### Name: R. Harini

### Dataset: Credit Card


* * *
```{r}
rm(list=ls())
library(dplyr)
library(ggplot2)
library(car)
library(caret)
```
```{r}
df=read.csv("CreditCard.csv", stringsAsFactors = TRUE)
```


* * *
#### 1. Display the structure of the data set.

```{r}

str(df)
```


#### 2. Print the bottom 10 observations in the data set.

```{r}
tail(df,10)
```

#### 3. Display the summary statistics of the variables income share and expenditure.
```{r}
summary(df$income)
summary(df$share)
summary(df$expenditure)
```

* * *
#### 4. Print the average income, median share and minimum expenditure for the applicants who do not own a house and had their application rejected.
```{r}
d=df%>%
  filter(owner=='no' & card=='no')
mean(d$income)
median(d$share)
min(d$expenditure)
```
#### 5. Do a random sampling of 15 data and plot to observe any outlier in the income? Justify your answer by appropriate plot and inference.
```{r}
s=sample(df$income, size=15)
boxplot(s, main="Samples of Income")
```

##### Since there are points visible above the top-most horizontal line, we can infer that outliers are present in the Income variable



#### 6. Find the standard deviation of income
```{r}
sd(df$income)
```
#### 7. Create a new column called income_cat which would have 3 labels as low, medium and high according to the income <=2.5, income >=2.5 and income<=4 and age>4 respectively.
```{r}
newdf=df%>%
  mutate(income_cat=case_when(income<=2.5~"low",
                   income>=2.5 & income<=4~"medium",
                   income>4~"high"))
colnames(newdf)
head(newdf$income_cat,10)
```



#### 8. Identify which income category applicants have their applications mostly rejected.
```{r}
t=newdf%>%
  filter(card=="no")
max(table(t$income_cat))
which.max(table(t$income_cat))[1]

```
##### The Low income category applicants have their applications mostly rejected. (freq= 142)

#### 9. Is there any low income self-employed applicants with own house got their application accepted?
```{r}
newdf%>%
  filter(income_cat=="low" & owner=="yes" & selfemp=="yes" & card=="yes")
```
##### Yes there are 5 people satisfying all the conditions.
* * *
#### 10. What is the frequency and relative frequency distribution of applicants owning and not owning house?
```{r}
freq=table(df$owner)
freq
rel_freq=freq/nrow(df)
rel_freq
```

#### 11.  Provide visualization of frequency distribution of applicants owning and not owning house.
```{r}
ggplot(df, aes(x=owner, fill=owner))+geom_bar()+ggtitle("Frequency distribution of the owners")+xlab("Owning the house: Yes or No")+ylab("Frequency")
```

#### 12. Does the income and expenditure of the applicants correlated? Justify your answer.
```{r}
cor(df$income, df$expenditure)
```
##### The variables are mildly correlated as the correlation coefficient is above 0 but still well below 0.5.

* * *
#### 13. Predict the value of expenditure based on other numerical values and compare various models with different combination of variables. Suggest a model with limited dependent variables that is better according to you. Justify your analysis.
```{r}
# Drop the ID column
data=df[,2:13]

set.seed(123)
train_samples <- data$expenditure %>%
  createDataPartition(p=0.8,list=FALSE)

train <- data[train_samples,]
test <- data[-train_samples,]

model1=lm(expenditure~.,data=train)
summary(model1)

```
```{r}
pred=model1%>%
  predict(test)
```

```{r}
RMSE(pred,test$expenditure)
```
```{r}
R2(pred,test$expenditure)
```

```{r}
confint(model1)
```
```{r}
vif(model1)
```
##### Since all the values are less than 5, we needn't remove any variables yet.


#### Model 2
```{r}
#Removing the least significant variables from the model
model2=lm(expenditure~.-selfemp-card-majorcards, data=train)
summary(model2)
```
```{r}
pred2=model2%>%
  predict(test)
```

```{r}
RMSE(pred2, test$expenditure)
```
```{r}
R2(pred2,test$expenditure)
```
#### Model 3
```{r}
model3=lm(expenditure~
            age+dependents+months+active,data=train)
summary(model3)
```
```{r}
pred3=model3%>%
  predict(test)
```

```{r}
RMSE(pred3, test$expenditure)
```
```{r}
R2(pred3, test$expenditure)
```
#### Model 4
```{r}
model4=lm(expenditure~log(share)*age*income*dependents,data=train)
summary(model4)
```
```{r}
pred4=model4%>%
  predict(test)
```

```{r}
RMSE(pred4,test$expenditure)
```
```{r}
R2(pred4,test$expenditure)
```


#### Model 5
```{r}
# Using only the most significant variables from model 1
model5=lm(expenditure~
            income*share*months*active, data=train)
summary(model5)
```

```{r}
pred5=model5%>%
  predict(test)
```

```{r}
RMSE(pred5,test$expenditure)
```
```{r}
R2(pred5,test$expenditure)
```

```{r}
model6=lm(expenditure~
            card*income*selfemp*majorcards,data=train)
summary(model6)
```
```{r}
pred6=model6%>%
  predict(test)
RMSE(pred6,test$expenditure)
R2(pred6,test$expenditure)
```

### On comparing the 6 models, Model 5 performed the best with its high Adjusted R-Squared (1) and low RMSE (0.32) as compared with other models.

```{r}
# You can view the points following the line in the first plot.
plot(model5,1)
plot(model5,2)
plot(model5,3)
plot(model5,4)

```

