---
title: "Assessment 1"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010

### Name:R. Harini

### Frame any 10 questions for data manipulation


* * *
Your Question here
```{r}
rm(list=ls())
library(MASS)
library(dplyr)
library(ggplot2)
df=Pima.tr
```


* * *
### Data Manipulation


```{r}
str(df)
colnames(df)
```

#### 1. Display npreg and age of people with type Yes
```{r}
df%>%
  filter(type=="Yes")%>%
  dplyr::select(npreg, age, type)
```

#### 2. Find the max bmi who have diabetes type as Yes
```{r}
df%>%
  filter(type=="Yes")%>%
  summarise(max(bmi))
```

#### 3. Create a new variable which is the average of glu and bp and add it to the dataset
```{r}
df=df%>%
  mutate(g_b=(glu+bp)/2)
df
```

#### 4. Arranging the dataset in descending order according to age for all type "Yes"
```{r}
arrange(df, desc(age))%>%filter(type=="Yes")
```

#### 5. Find the standard deviation of bp for type Yes and No
```{r}
df%>%
  group_by(type)%>%
  summarise(sd(bp))
```

#### 6. Display bp and glu of those who have type Yes and age above 30
```{r}
df%>%
  filter(type=="Yes" & age>30)%>%
  dplyr::select(bp, glu, type, age)
```

#### 7. Find the average of bp, glu for people with age below 30 and bmi above 30 with type Yes and No
```{r}
df%>%
  filter(age<30 & bmi>30)%>%
  group_by(type)%>%
  summarise(mean(bp), mean(glu))
```

#### 8. Display the variance of bmi for people with npreg above the average npreg and skin below 20
```{r}
df%>%
  filter(npreg>mean(npreg) & skin<20)%>%
  summarise(var(bmi))

```

#### 9. Arrange the dataset in ascending order of bmi with skin below 25 and ped above 1
```{r}
arrange(df, bmi)%>%
  filter(skin<25 & ped>1)
```


#### 10. Group the dataset based on Type for all those who have age higher than the mean and find the variance of bp

```{r}
df%>%
  group_by(type)%>%
  filter(age>mean(age))%>%
  summarise(var(bp))
```


* * *
### Visualisation

#### 1. Visualising the range of Age
```{r}
hist(df$age, main="Range of Age", xlab = "Age", col = "light blue")
```

#### 2. Visualising the frequency of Type Yes and No
```{r}
c=df%>%
  group_by(type)%>%
  tally()
c
barplot(c$n, main="Frequnecy of Type", names.arg = c$type, col=c("blue", "red"))
```

#### 3. visualising the summary statistics of bp
```{r}
summary(df$bp)
boxplot(df$bp, main="Summary Statistics of bp")
```


#### 4. Scatter plot between Glu and Skin
```{r}
plot(df$glu, df$skin, main = "Scatter Plot between Glue and Skin", xlab = "Glucose", ylab="Skin", col="green")
```


#### 5. Scatter plot between BMI and Ped for each Type
```{r}
ggplot(df, aes(x=bmi, y=ped))+geom_point()+facet_wrap(~type)+labs(title="BMI vs Ped")
```

#### 6. A Pie Chart for number of Yes and No taking npreg as the levels
```{r}
ggplot(df, aes(x=npreg,y=type, fill=type))+geom_bar(stat="identity", width=1)+coord_polar("y", start=0)

```

#### 7. Density plot of Bp
```{r}
d=density(df$bp)
plot(d, main="Density plot for BP")
```

#### 8. Creating the scatter Plot for Bp, Bmi with varying size based on Ped
```{r}
ggplot(df, aes(x=bp, y=bmi, size=ped, col="red"))+geom_point()+labs(title = "Bp vs bmi with Ped")
```

#### 9. Creating a Scatter Plot between Glu and Age with Type as Shape
```{r}
ggplot(df, aes(x=glu, y=age, shape=type))+geom_point()+labs(title = "Age vs Glucose For different types")
```

#### 10. Adding a best fit line to Skin vs Age
```{r}
ggplot(df, aes(x=skin, y=age))+geom_point()+geom_smooth(method = 'lm')+labs(title="Skin vs Age")
```



