---
title: "18BCE1010_Ast2"
output: html_document
---

## Name: R. Harini

## Regn No: 18BCE1010

## Dataset: Biopsy Data on breast Cancer Patients

```{r}
library(MASS)
library(dplyr)
library(ggplot2)
```

```{r}
rm(list=ls())
```

```{r}
data=biopsy
str(data)
summary(data)
sum(is.na(data$V6))
data=data%>%mutate(V6=replace(V6, is.na(V6), mean(V6, na.rm = TRUE)))
sum(is.na(data))
```
### 1. Frequency and Relative Frequency Distribution of Benign and Malignant categories
```{r}
freq=table(data$class)
rel_freq=freq/nrow(data)

freq
rel_freq
```

### 2. Show frequency distribution graphically by bar chart
```{r}
barplot(freq,main="Freq distribution of Benign and Malignant", ylab="Frequency", col=c("blue", "red"))
```

### 3. Frequency dsitribution of clump thickness
```{r}
clump_freq=table(data$V1)
cbind(clump_freq)
```

### 4. Mean clump thickness of benign and malignant categories
```{r}
data%>%
  group_by(class)%>%
  summarize(mean(V1))
```
### 5. Most Frequently occurring single epithelial cell size
```{r}
table(data$V5)
which.max(table(data$V5))
```
#### The most frequency occurring cell size is 2

### 6. Interquartile Range of epithelial cell size
```{r}
IQR(data$V5)
```

### 7. Checking correlation between clump thickness and epithelial vell size
```{r}
cor(data$V1, data$V5)
```
#### Since the correlation is >0, it is postively correlated.

### 8. Checking the skewness of clump thickness
```{r}
library(e1071)
skewness(data$V1)
```
#### The data is positively skewed/ right-skewed as it is >0

### 9. Predict the value of clump thickness based on other numerical values and compare models
```{r}
library(caret)
library(car)
data=data[,2:11] #Dropped the ID column

set.seed(123)
train_samples <- data$V1 %>%
  createDataPartition(p=0.8,list=FALSE)

train <- data[train_samples,]
test <- data[-train_samples,]

model1=lm(V1~.,data=train)
summary(model1)
pred=model1%>%
  predict(test)
```

```{r}

confint(model1)
RMSE(pred,test$V1)
R2(pred,test$V1)
```
```{r}
vif(model1)
```
```{r}
model2=lm(V1~.-V2, data=train)
pred2=model2%>%
  predict(test)
RMSE(pred2,test$V1)
R2(pred2,test$V1)

```
```{r}
model3=lm(V1~.-V2-V3,data=train)
pred3=model3%>%
  predict(test)
RMSE(pred3,test$V1)
R2(pred3,test$V1)
```
```{r}
model4=lm(V1~V4*V5, data=train)
pred4=model4%>%
  predict(test)
RMSE(pred4,test$V1)
R2(pred4,test$V1)
```
```{r}
model5=lm(V1~V4+V5,data=train)
pred5=model5%>%
  predict(test)
RMSE(pred5,test$V1)
R2(pred5,test$V1)
```

#### On comparing 3 models, the third model which has dropped the variables V2 and V3 perform the best. The conclusion has been reached by comparing the R2 and RMSE of the models. Model 3 has the highest R2 (0.508) and the lowest RMSE(1.99)
```{r}
plot(model3,1)
plot(model3,2)
plot(model3,3)
plot(model3,4)
```

