---
title: "Review1 - Exploring and Analyzing Online Rental Company Data to Gain Sights"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010

### Name: R. Harini



* * *

## What problem are you trying to solve?

For a decade now, people have used Airbnb to expand traveling possibilities and present a personalized way of exploring the world. 

With the current scenario of COVID-19, hotels all around the world are a facing a decline in their profits. 
 
Due to this, extracting important information from the previously provided data becomes extremely crucial in order to enhance the business. With the inferences gained from analyzing this data one can concentrate on the area which bring in maximum customers and gain higher profits.

The dataset depicts the listing activity and metrics in New York for 2019.


* * *



* * *

## What data have you chosen?(Chosen Dataset, Source of dataset, Description of dataset, basic commands to describe dataset)

#### Chosen Dataset: Airbnb Listings for New York in 2019

Dataset taken from insideairbnb.com

48895 x 16 csv file

Includes columns such as Id, Name, Host ID, Longitude, Latitude, Number of reviews, Price, etc.

```{r}
data=read.csv("AB_NYC_2019.csv")
head(data)
```

```{r}
colnames(data)
```


```{r}
dim(data)
```
```{r}
typeof(data)
```
```{r}
summary(data)
```
```{r}
str(data)
```


* * *

* * *

## Frame your objectives

~ Learning about different hosts and areas
~ Learning from the trends in prices and reviews
~ Which location is the busiest and has the maximum number of reviews?
~ Which group generates maximum revenue?
~ Visualizing the distribution of the income 
~ Frequency distribution of neighborhood and room types
~ Building a regression model to predict Prices


* * *

## Is there any work previously reported on the problem and the data? If so, discuss it here.

Data Analysis has been conducted on Airbnb Seattle dataset. However in this project I will be using Airbnb New York dataset as well as building a Machine Learning model on it. 


* * *



