---
title: "Project Review: Using Airbnb Dataset"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010


### Name: R. Harini


### Chosen Dataset: New York City Airbnb Open Data

#### For a decade now, people have used Airbnb to expand travelling possibilities and present a personalized way of exploring the world. This dataset depicts the listing activity and metrics in NYC, NY for 2019.

### Exploration Possibilities:

#### ~Learning about different hosts and area

#### ~Learning from predictions of prices and reviews

#### ~Which location is th busiest and has maximum number of reviews?

#### ~Which group generates maximum revenue?


## Setup
```{r}
rm(list=ls())
```


### Load packages if any using library(packagename)
```{r}
library(dplyr)
```



### Load data
```{r}
#data(iris) A sample is shown here
data=read.csv("AB_NYC_2019.csv")
```



* * *



```{r}
head(data)
```
```{r}
colnames(data)
```

```{r}
dim(data)
```


```{r}
ncol(data)
nrow(data)
```

```{r}
class(data)
```
```{r}
typeof(data)
```

```{r}
summary(data)
```

```{r}
str(data)
```




