---
title: "LabEx7-Analysis of Variance (ANOVA)"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010

### Name: R. Harini

## Setup
```{r}
rm(list=ls())
```


### Load packages if any using library(packagename)
```{r}
library(dplyr)
library(ggplot2)
library(car)
library(ggpubr)
```


### Load data
```{r}
data=read.csv("heart.csv")

colnames(data)[1]="age"
colnames(data)

#Converting the required columns to factors
str(data)
data=data%>%
  mutate(sex=replace(sex, sex==1, "Male"))
data=data%>%
  mutate(sex=replace(sex, sex==0, "Female"))
data=data%>%
  mutate(target=replace(target, target==1, "Yes"))
data=data%>%
  mutate(target=replace(target, target==0, "No"))
data$sex=as.factor(data$sex)
data$target=as.factor(data$target)
data$slope=as.character(data$slope)
data$slope=as.factor(data$slope)
str(data)

```

* * *
### Checking for Significant Difference b/w Average Trestbps with different Target (1-way ANOVA)
##### Assuming that the variables have normal distribution
```{r}
levels(data$target)
data%>%
  group_by(target)%>%
  summarize(count=n(),mean=mean(trestbps), std_dev=sd(trestbps))

```
```{r}
ggplot(data, aes(x=target, y=trestbps))+geom_boxplot()
```

```{r}
ggline(data, x="target",y="trestbps", add=c("mean_se"), ylab="Trestbps", xlab = "Target")
```


```{r}

res=aov(trestbps~target,data=data)
summary.aov(res)
```


#### Checking Homogeneity of Variance
```{r}
plot(res,1)
leveneTest(trestbps~target, data)
```

#### Checking normality Assumptions
```{r}
plot(res,2)

resi=residuals(res)
shapiro.test(resi)
```

#### Non Parametric Alternative as Assumptions arent met
```{r}
kruskal.test(trestbps~slope, data)
```

* * *

### What is your inference for one-way ANOVA test?
* * *
```{r}
## Since the p-value (0.0115) is less than 0.05, we can say that there is a significant difference between the groups.

## Although there is only one pair, I have still tried out the TukeyHSD to see what result it shows.

## However in Levene's test we can see that the p-value (0.174)>0.05, therefore there is no significance level of variance between the gorups.

## In Shapiro-test, the p-value is less than 0.05 significance level, implying there exists significant difference from normal distribution, we can assume there exists no normality

## Therefore performing Kruskal-Wallis rank sum test as ANOVA assumptions arent met.
```


 
* * *
### Checking for the effect of Slope and Sex on Chol (2-way ANOVA)

#### Summary Statistics
```{r}
levels(data$sex)

data%>%
  group_by(sex, slope)%>%
  summarise(count=n(), mean=mean(chol), std_dev=sd(chol))

```

#### Plotting
```{r}
ggboxplot(data, x="slope", y="chol", color = "sex", pallete=c("green", "blue"))

```

####Computing 2-way ANOVA using additive model
```{r}
res2=aov(chol~sex+slope, data)
summary.aov(res2)
```

####Computing 2-way ANOVA using interactions
```{r}
res3=aov(chol~sex*slope, data)
summary.aov(res3)
```

#### Performing TukeyHSD
```{r}
TukeyHSD(res2, which="sex")
```

#### Checking Homogeneity
```{r}
plot(res2, 1)

leveneTest(chol~sex*slope, data)
```

#### Checking normality
```{r}
plot(res2, 2)

res2_resi <- residuals(res2)
shapiro.test(res2_resi)

```

#### Computing 2-way ANOVA test for unbalanced designs
```{r}
ao=aov(chol~sex*slope, data)
Anova(ao, type="III")
```


* * *

### What is your inference for two-way ANOVA test  
* * *
```{r}
## Since the p-value (0.000542 ***) is less than 0.05, we can say that there is a significant difference between the groups.

## Although there is only one pair, I have still tried out the TukeyHSD to see what result it shows.

## However in Levene's test we can see that the p-value (0.08839)>0.05, therefore there is no significance level of variance between the gorups.

## In Shapiro-test, the p-value is less than 0.05 significance level, implying there exists significant difference from normal distribution, we can assume there exists no normality
```


* * *

### Frame a question for MANOVA and do the analysis 
* * *
```{r}
res3=manova(cbind(trestbps, chol)~sex, data=data)
summary.aov(res3)
```

### What is your inference for  MANOVA test  

```{r}
### Since the p-value for trestbps  (0.3247)>0.05, we can say there there is no significant level of difference of Trestbps in the Sex groups.

## However the p-value of chol (0.00053 ***) <0.05, we can say that there is a significant level of difference of Chol in the sex groups.
```

* * *




