---
title: "LabEx6-Descriptive statistics and Visualization in R"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010

### Name: R. Harini

## Setup
```{r}
rm(list=ls())
```


### Load packages if any using library(packagename)
```{r}
library(dplyr)
library(MASS)
library(e1071)
library(ggplot2)
```



### Load data
```{r}
data=read.csv("heart.csv")
colnames(data)[1]="age"
colnames(data)

#Converting the required columns to factors
str(data)
data=data%>%
  mutate(sex=replace(sex, sex==1, "Male"))
data=data%>%
  mutate(sex=replace(sex, sex==0, "Female"))
data=data%>%
  mutate(target=replace(target, target==1, "Yes"))
data=data%>%
  mutate(target=replace(target, target==0, "No"))
data$sex=as.factor(data$sex)
data$target=as.factor(data$target)
data$slope=as.character(data$slope)
data$slope=as.factor(data$slope)
str(data)

sum(is.na(data))
```
### Frame a minimum of 3 questions for qualitative data analysis and provide appropriate visualization
* * *
#### 1. Number of Male and Female Participants who had heart disease
```{r}
d=data%>%
  filter(target=="Yes")
freq=table(d$sex)
cbind(freq)

barplot(freq, main="Male and Female participants with heart disease", ylab = "frequency", col=c("blue", "red"), names.arg = levels(d$sex))

```

#### 2.Relative frequency distribution of the slope
```{r}

freq=table(data$slope)
rel=freq/nrow(data)
round(rel,2)
pie(round(rel,2))
```


#### 3. Percentage of Females who suffer from Heart Disease
```{r}
c=data[which(data$sex=="Female" & data$target=="Yes"),]
perc=nrow(d)/nrow(data)*100
perc
```

* * *


* * *


### Frame a minimum of 5 questions for quantitative data analysis and provideappropriate visualization
* * *
#### 1. Find the range of Age
```{r}
range(data$age)
hist(data$age, main="Histogram of Age")
```

#### 2. Frequency distribution of Age
```{r}
breaks <- seq(28,78,by=5)
age_split=cut(data$age, breaks,right=FALSE)
freq=table(age_split)
cbind(freq)
barplot(freq, main="Frequency distribution of Age")
```

#### 3. Finding range of chol and finding the relative frequency
```{r}
range(data$chol)
breaks=seq(126,566,by=20)
chol_split=cut(data$chol, breaks, right=F)
chol_freq=table(chol_split)
chol_rel=round(chol_freq/nrow(data),2)
chol_rel
barplot(chol_rel, main="Relative frequency distribution of Chol")
```

#### 4. Finding cumulative frequency distribution of trestbps
```{r}
range(data$trestbps)
breaks=seq(90,200,by=20)
tres_split=cut(data$trestbps, breaks, right = F)
tres_freq=table(tres_split)
cumsum(tres_freq)
hist(data$trestbps, main="Histogram of trestbps")
```

#### 5. Finding cumulative relative frequency distribution of thalach
```{r}
range(data$thalach)
breaks=seq(70,210,by=20)
thal_split=cut(data$thalach, breaks, right=F)
thal_freq=cbind(table(thal_split))
thal_freq
cumsum(thal_freq)/nrow(data)
hist(data$thalach,main="Histogram of Thalach")
```



* * *


### Frame a minimum of 5 questions for numerical measures analysis and provide appropriate visualization

* * *
#### 1. Finding the moments of trestbps of people who have heart disease
```{r}
d=data%>%
  filter(target=="Yes")
moment(d$trestbps, order=3, center=TRUE)
ggplot(d, aes(x=trestbps))+geom_density()
```

#### 2. Finding kurtosis of thalach of people who have heart disease
```{r}
kurtosis(d$thalach)
hist(d$thalach, main="Hist of thalach with target='Yes'")
```

#### 3. Finding the skewness in Chol of people who have heart disease
```{r}
skewness(d$chol)
ggplot(d, aes(x=chol))+stat_density(geom="line", alpha=1, colour="blue")

```

#### 4. Finding statistical measure of oldpeak of people who have heart disease
```{r}
summary(d$oldpeak)
boxplot(d$oldpeak)
```

#### 5. Finding the average age of males who do not have heart disease
```{r}
c=data%>%
  filter(target=="No" & sex=='Male')
mean(c$age)
boxplot(c$age)
```



* * *





