---
title: "LabEx3-Data Manipulation using dplyr package"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 18BCE1010

### Name: R. Harini

## Setup
```{r}
rm(list=ls())
```


### Load packages if any using library(packagename)
```{r}
library(MASS)
library(dplyr)
```



### Load data
```{r}
#data(iris) A sample is shown here
data("quakes")
data=quakes
```




* * *

## Ignore this part if there is no change in the data set previously chosen. Otherwise, notify it here.  (Chosen Dataset, Description of dataset, basic commands to describe dataset)

### Chosen Dataset: Quakes

### Description: The dataset contains 1000 observations of earthquake data that occurred near the tropical island of Fiji. Each observation has the latitude, longitude, depth, magnitude and number of stations that reported the seismic activity

```{r}
head(data)
```

```{r}
colnames(data)
```
```{r}
ncol(data)
nrow(data)
```


```{r}
summary(data)
```

```{r}
str(data)
```

```{r}
dim(data)
```

* * *

##  Selected Questions and Corresponding Code & Output

```{r}
#1. Displaying the latitude and longitudes of the area with depth above 400
data%>%
  filter(depth>400)%>%
  dplyr::select(lat, long, depth)

```

```{r}
#2. Display the number of stations where maximum magnitude of earthquake occurred.
data%>%
  filter(mag==max(mag))%>%
  dplyr::select(stations, mag)
```
```{r}
#3. Display the number of stations with longitude below 150
data%>%
  filter(long<170)%>%
  dplyr::select(stations, long)
```

```{r}
#4. Arrange the entire dataset based on descending order of the magnitude
arrange(data, desc(mag))
```

```{r}
#5. Create a new variable that sums up latitude and longitude and filter the rows with mag>5
data%>%
  mutate(newvar=long+lat)%>%
  filter(mag>5)
```


```{r}
#6. Display the mean of the number of the stations with magnitude above 5
data%>%
  filter(mag>5)%>%
  summarise(mean(stations))
```
```{r}
#7. Display the latitudes, longitudes and magnitudes of the regions with depth above 300 in descending order og magnitude
data%>%
  filter(depth>300)%>%
  dplyr::select(lat,long,mag, depth)%>%
  arrange(desc(mag))
```
```{r}
#8. Display the mean of magnitude with depth less than 300 and number of stations more than the mean
data%>%
  filter(depth<300 & stations>mean(stations))%>%
  summarise(mean(mag))
```
```{r}
#9. Display the depth of regions with latitude below -15 and longitude above 150
data%>%
  filter(lat<-15 & long>150)%>%
  dplyr::select(lat, long,depth)
  
```


```{r}
#10. Add a new variable which is the average of depth and stations
data%>%
  mutate(avg=rowMeans(data[,c(3,5)]))
```


```{r}

```


* * *



